Which spherical CNN should you use?\\ DeepSphere V2

### 2019-09-03 main.tex
Updates from Overleaf

\begin{table}[!ht]
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        Jiang (bsize 64) & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
        % 328'339
        Cohen et al. (S2R) & - & -& 68.6 & - & - \\
        Cohen et al. (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (ico) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 ms & 13h \\ \hline
        % DS (non-weighted) & 83.66 & 97.57 & 90.62 & 30ms & 13h\\ \hline
        % 12'926'432
        DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as wel, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

trade off between AP and accuracy in the case of TC class, it seems.

@@

dense regression
\begin{table}[!ht]
    \centering
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 10.88 & 2.42 & 0.896\\
        1 & 8.91 & 2.20 & 0.906\\
        4 & 8.20 & 2.11 & 0.919\\
        9 & 8.38 & 2.12 & 0.915\\
    \end{tabular}
    \caption{The task is to find the temperature for the day T, knowing the temperature of the 5 previous days. Evolution of performance in respect of the order of the filter}
    \label{tab:future_results}
    ~\\[1cm]
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        1 & 134.01 & 10.51 & -0.319\\
        4 & 129.48 & 10.31 & -0.274\\
        9 & 141.68 & 10.82 & -0.389\\
    \end{tabular}
    \caption{Predicting the present day (T-1) instead of the future day T}
    \label{tab:present_results}
\end{table}

global regression
\begin{table}[!ht]
    \centering
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 0.58 & 0.42 & -0.92\\
        4 & 0.50 & 0.18 & 0.597\\
    \end{tabular}
    \caption{Find day in year using precipitation}
    \label{tab:glob_prec}
    ~\\[1cm]
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 0.10 & 0.10 & 0.881\\
        4 & - & - & -\\
    \end{tabular}
    \caption{Using temperature feature that are already periodical}
    \label{tab:glob_all}
\end{table}

@@

* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
  * scales linearly => cannot do better ($n^1.25$ for best HEALPix, linear for not optimal)\\
  * flexible => independent of the sampling\\

@@

concat the results of the corresponding encoder layer after the pooling. Not similar to Jiang and 4 times the feature maps.

@@

30 epochs
\subsubsection*{Correct Icosahedron}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
number of parameters: 590'976  % more feat is 16 times more

>>>>

\begin{table}[!ht]
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        Jiang (bsize 64) & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
        % 328'339
        Cohen et al. (S2R) & - & -& 68.6 & - & - \\
        Cohen et al. (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (ico) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 ms & 13h \\ \hline
        % DS (non-weighted) & 83.66 & 97.57 & 90.62 & 30ms & 13h\\ \hline
        % 12'926'432
        % non-weighted: accuracy (99.28, 33.60, 93.56, mean: 75.4819);AP (46.15, 93.87, mean: 70.01)
        % weighted:        accuracy (96.52, 97.13, 97.59, mean: 97.08); AP (49.71, 89.23, mean: 69.47)
        DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as wel, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

* trade off between AP and accuracy in the case of TC class, it seems.\\
* change base, influence\\
*

@@

* non-regular sampling with different density over the globe (continent vs ocean)\\
* resulting graph is not rotation equivariant\\
* Two different tasks: a dense regression and a global regression\\

\subsubsection*{dense regression - future temperature estimation}
* Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
* Goal is to change the order of the chebyshev filter to find the influence of the structure.\\
* order 0 is the same as time series, as the pixel have no information of its neighborhood.\\
* increasing order is good until threshold.\\
* The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference.\\

\begin{table}[!ht]
    \centering
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 10.88 & 2.42 & 0.896\\
        1 & 8.91 & 2.20 & 0.906\\
        4 & 8.20 & 2.11 & 0.919\\
        9 & 8.38 & 2.12 & 0.915\\
    \end{tabular}
    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
    \label{tab:future_results}
    \end{minipage}
    \hfill
    %~\\[1cm]
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        1 & 134.01 & 10.51 & -0.319\\
        4 & 129.48 & 10.31 & -0.274\\
        9 & 141.68 & 10.82 & -0.389\\
    \end{tabular}
    \caption{Baseline: testing with the present day (T-1) instead of the future day T}
    \label{tab:present_results}
    \end{minipage}
\end{table}

\subsubsection*{global regression - day in year estimation}
* days represented by a sine to represent the periodic nature of the year.\\
* task too easy, features already periodic\\
* structure is still helping\\

\begin{table}[!ht]
    \centering
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 0.58 & 0.42 & -0.92\\
        4 & 0.50 & 0.18 & 0.597\\
    \end{tabular}
    \caption{Find day in year using precipitation}
    \label{tab:glob_prec}
    \end{minipage}
    \hfill
    %~\\[1cm]
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 0.10 & 0.10 & 0.881\\
        4 & 0.05 & 0.05 & 0.969\\
    \end{tabular}
    \caption{Using temperature feature that is already periodical}
    \label{tab:glob_all}
    \end{minipage}
\end{table}

@@

* DeepSphere seems to be in the sweet spot of tradeoffs. Recall the desiderata.\\
  * respect geometry: No need for a very precise equivariance, i.e. a very good graph...\\
  * Not the most general (restricted to isotropic filters), but didn't hurt perf in any experiment\\
  * scales linearly => cannot do better ($n^{1.25}$ for best HEALPix, linear for not optimal)\\
  * flexible => independent of the sampling\\

@@

concat the results of the corresponding encoder layer before the graph convolution. Not similar to Jiang and 4 times the feature maps.

@@

30 epochs
\subsubsection*{Jiang Icosahedron}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
number of parameters: 590'976  % more feat is 16 times more
